\documentclass[11pt,letterpaper,roman]{moderncv}
\moderncvtheme[red]{classic}

\usepackage[scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{0.15\textwidth}
\usepackage{mathpazo}
\renewcommand{\sfdefault}{\rmdefault}
\AtBeginDocument{\recomputelengths}

\firstname{Morgan}
\familyname{Kesler}
\mobile{(813) 316-3833}
\email{keslerm@dasbiersec.com}
\homepage{www.dasbiersec.com}

\nopagenumbers{}

\begin{document}

\maketitle

\section{Skills}
	\cvline{Languages:}{Java, Ruby, Python, C\#, PHP}
	\cvline{Databases:}{PostgreSQL, MySQL, MSSQL}
	\cvline{VCS:}{Git, Mercurial, Subversion}
	

\section{Experience}
	\cventry{2010-Current}{Java Developer}{Kobie Marketing}{St Petersburg, FL}{}{
		\begin{itemize}
			\item Designed and built multiple new implementations for clients in the telecommunications, retail and financial services space using REST and SOAP based web services, flat files and databases handling 1,000,000+ transactions monthly.
			\item Using SQL, Java and Talend built ETL and data aggregation processes for customer reporting on large data sets, along with optimizing existing processes to handle large data sets more efficiently to reduce run time.
			\item Wrote test cases and utilized unit testing with JUnit to ensure programs follow supplied business requirements.
			\item Participated in ongoing initiatives to improve processes for existing loyalty clients and establish best practices for the entire IT department.
      \item Redesigned existing file processing systems that greatly improved efficiency, run times and reducing the number of manual hours each month by over 80\%.
      \item Outlined and deployed process for upgrading existing clients running on legacy Jboss 4/Postgres 8 platform to the new Jboss 7/Postgres 9 platform.
      \item Spearheaded the initiative to migrate our existing stand alone Subversion version control system to the Git based Atlassian Bitbucket Server to improve code management and peer review processes.
      \item Developed a system for a unique telecom client involving direct mail promotions that reduced development time around new promotions by more than half.
		\end{itemize}
	}

	\cventry{2007-2010}{Web Developer}{GPS Fleet Solutions}{Wesley Chapel, FL}{}{
		\begin{itemize}
			\item Designed and developed a highly customized customer portal with trouble ticketing, online quoting, ordering, inventory and shipment tracking to move business from a paper based to online.
			\item Designed, developed and maintained companies consumer facing website using CakePHP and MySQL along with integrating it with SugarCRM for lead management.
			\item Developed integration with Google Maps API with PHP, MySQL, and SQL Server to output raw GPS data routes and points on a web based map, along with automated Geo-Fencing alerts.
			\item Wrote SQL scripts to compile GPS data into reports that outlined miles traveled, alerts generated, hours running, hours idling, and PTO usage using SQL Server.
			\item Integrated multiple vendors GPS tracking systems into internal customer portal for web based mapping and single sign on functionality using MS SQL and REST based web services.
			\item Converted an ACT! MS SQL CRM system to a SugarCRM MySQL system using a custom ETL tool for data mapping, along with integrating SugarCRM with the internal customer portal.
		\end{itemize}
	}

\section{Extra}
	\cvlistitem{GitHub Contributor - see \url{https://github.com/keslerm}}
\end{document}
